Exploring dimensions of biodiversity in Japanese ferns

### 2021-07-08 ms/SI.Rmd
Fix paths to bibliography problem

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
bibliography: 
  - references.yaml
  - references_other.yaml
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

@@

```{r phy-sig}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*K*` = kval,
    `λ` = lambda,
    `*p* (*K*)` = k_pval,
    `*p* (λ)` = lambda_pval,
    `*n*` = n
    ) %>%
  as_flextable() %>%
  colformat_md(part = "all")
```

@@

```{r phy-sig-binary}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*n* (present)` = num_present,
    `*n* (absent)` = num_absent,
    `*p* (random)` = prob_random,
    `*p* (Brownian)` = prob_brownian
    ) %>%
  as_flextable() %>%
  colformat_md(part = "all")
```

@@

```{r lrt-null}
lrt_results %>%
  filter(comparison == "null_model") %>%
  select(-null_formula, -comparison) %>%
  tidyr::extract(full_formula, "model_type", "~ ([^ ]+) ") %>%
  rename_resp_vars %>%
  rename_model_type %>%
  select(model_type, resp_var, chi2_LR, df, loglik_null, loglik_full, p_value) %>%
  arrange(model_type, resp_var) %>%
  mutate(across(where(is.double), ~format(., digits = 2))) %>%
  # colformat_md() doesn't work on grouped tables
  # group_by(model_type) %>%
  # as_flextable(hide_grouplabel = TRUE) %>%
  rename(
    Response = resp_var,
    `Model type` = model_type,
    `χ^2^` = chi2_LR,
    `logL (full model)` = loglik_full,
    `logL (null model)` = loglik_null,
    `*p*` = p_value
  ) %>%
  as_flextable %>%
  merge_v(j = "Model type") %>% 
  valign(valign = "top") %>% 
  colformat_md(part = "all")
```

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
date: '`r format(Sys.time(), "%d %B, %Y")`'
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
header-includes: 
  \usepackage{float}
  \makeatletter\renewcommand*{\fps@figure}{H}\makeatother
editor_options: 
  chunk_output_type: console
params:
  doc_type: pdf
# nocite: | 
---

---
bibliography:
  - `r here::here("ms/references.yaml")`
  - `r here::here("ms/references_other.yaml")`
---

@@

```{r phy-sig, results = "as-is"}
phy_sig_results %>%
  mutate(across(c(kval, lambda, k_pval, lambda_pval), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*K*` = kval,
    `λ` = lambda,
    `*p* (*K*)` = k_pval,
    `*p* (λ)` = lambda_pval,
    `*n*` = n
    ) %>%
  as_flextable() %>%
  autofit() %>%
  colformat_md(part = "all")
```

@@

```{r phy-sig-binary, results = "as-is"}
binary_sig_results %>%
  select(trait, D, num_present, num_absent, prob_random, prob_brownian) %>%
  arrange(trait) %>%
  mutate(across(c(D, prob_random, prob_brownian), ~format(., digits = 2))) %>%
  rename(
    ` ` = trait,
    `*n* (present)` = num_present,
    `*n* (absent)` = num_absent,
    `*p* (random)` = prob_random,
    `*p* (Brownian)` = prob_brownian
    ) %>%
  as_flextable() %>%
  fontsize(size = 7, part = "all") %>%
  autofit() %>% 
  colformat_md(part = "all")
```

@@

```{r lrt-null, results = "as-is"}
lrt_results %>%
  filter(comparison == "null_model") %>%
  select(-null_formula, -comparison) %>%
  tidyr::extract(full_formula, "model_type", "~ ([^ ]+) ") %>%
  rename_resp_vars %>%
  rename_model_type %>%
  select(model_type, resp_var, chi2_LR, df, loglik_null, loglik_full, p_value) %>%
  arrange(model_type, resp_var) %>%
  mutate(across(where(is.double), ~format(., digits = 2))) %>%
  # colformat_md() doesn't work on grouped tables
  # group_by(model_type) %>%
  # as_flextable(hide_grouplabel = TRUE) %>%
  rename(
    Response = resp_var,
    `Model type` = model_type,
    `χ^2^` = chi2_LR,
    `logL (full model)` = loglik_full,
    `logL (null model)` = loglik_null,
    `*p*` = p_value
  ) %>%
  as_flextable %>%
  merge_v(j = "Model type") %>% 
  valign(valign = "top") %>% 
  fontsize(size = 7, part = "all") %>%
  autofit() %>%
  colformat_md(part = "all")
```

### 2021-07-08 ms/manuscript.Rmd
Update MS
change pagebreak() to \newpage
Output tables directly to pdf
Fix paths to bibliography problem

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
bibliography: 
  - references.yaml
  - references_other.yaml
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

@@

`r pagebreak()`

@@

Here we leverage this exceptionally rich dataset to analyze the geographic distribution of biodiversity in detail. We ask the following questions in our study system, the ferns of Japan: 1. How is biodiversity distributed? 2. How is biodiversity structured? 3. How well is biodiversity protected?

@@

All models were significant relative to null models without any fixed effects. The effect of temperature dominated (had the greatest absolute *t*-value) in environmental models (`r figure("coeff")`A--E), and % apomictic taxa dominated in reproductive models (`r figure("coeff")`F--G); temperature and % apomictic taxa were significant in each model where they were included, whereas other predictors (area, precipitation, precipitation seasonality) were not significant in some models. Richness showed a hump-shaped relationship with temperature, reaching maximum richness at intermediate temperatures (`r figure("modelfit")`A). Phylogenetic and functional diversity showed either moderately (SES of PD, SES of FD) to strongly (SES of RPD, SES of RFD) hump-shaped relationships with temperature (`r figure("modelfit")`B--E). SES of RPD showed a clear, linear decline with % apomictic taxa (`r figure("modelfit")`G); a similar pattern was detected in SES of PD, but with wider confidence intervals (`r figure("modelfit")`F). Conditional AIC was lower (indicating better model fit) in the reproductive model compared to the environmental model for SES of RPD, but not SES of PD.

>>>>

---
title: "Exploring dimensions of biodiversity in Japanese ferns"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::word_document2:
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
    toc: no
    number_sections: no
    reference_docx: template.docx
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "journal-of-biogeography.csl"]
params:
  doc_type: doc
editor_options: 
  chunk_output_type: console
---

---
bibliography:
  - `r here::here("ms/references.yaml")`
  - `r here::here("ms/references_other.yaml")`
---

@@

\newpage

@@

Here we leverage this exceptionally rich dataset to analyze the geographic distribution of biodiversity in detail. We ask the following questions in our study system, the ferns of Japan: 1. How is biodiversity distributed? 2. How is biodiversity structured? 3. What environmental and biological factors influence biodiversity? 4. How well is biodiversity protected?

@@

All models were significant relative to null models without any fixed effects `r s_table("lrt-null")`. The effect of temperature dominated (had the greatest absolute *t*-value) in environmental models (`r figure("coeff")`A--E), and % apomictic taxa dominated in reproductive models (`r figure("coeff")`F--G); temperature and % apomictic taxa were significant in each model where they were included, whereas other predictors (area, precipitation, precipitation seasonality) were not significant in some models. Richness showed a hump-shaped relationship with temperature, reaching maximum richness at intermediate temperatures (`r figure("modelfit")`A). Phylogenetic and functional diversity showed either moderately (SES of PD, SES of FD) to strongly (SES of RPD, SES of RFD) hump-shaped relationships with temperature (`r figure("modelfit")`B--E). SES of RPD showed a clear, linear decline with % apomictic taxa (`r figure("modelfit")`G); a similar pattern was detected in SES of PD, but with wider confidence intervals (`r figure("modelfit")`F). Conditional AIC was lower (indicating better model fit) in the reproductive model compared to the environmental model for SES of RPD, but not SES of PD.
